---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CellDEEP

<!-- badges: start -->
<!-- badges: end -->

The goal of CellDEEP is to ...

## Installation

You can install the development version of CellDEEP like so:

``` {r,echo = FALSE}

devtools::install_github("sii-scRNA-Seq/CellDEEP")

```

## Example

Before using, don't forget library it:

```{r example}
library(CellDEEP)
```

To quickly run CellDEEP, just need to prepare the data, then run `FindMarker.CellDEEP`:

```{r cars, eval=FALSE}
pdc <- prepare_data(sample, sample_id = "sample_id", group_id = "Worst_Clinical_Status", cluster_id = "initial_clustering")

de.test <- FindMarker.CellDEEP(pdc, Pool = TRUE, ident.1 = "Healthy", ident.2 = "Severe", group.by = "group_id", n_cells = 6, cell_cutoff = 10)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
