---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CellDEEP

<!-- badges: start -->
<!-- badges: end -->

The goal of CellDEEP is to ...

## Installation
You can install the development version of CellDEEP like so:

Please download the package from github directly, then load the Rproject file.

``` {r,eval=FALSE}
#This is not working for now
devtools::install_github("sii-scRNA-Seq/CellDEEP")

```

## Example

Before using, don't forget library it:

```{r example}
library(CellDEEP)

library(devtools)
load_all()
```

To quickly run CellDEEP, just need to prepare the data, then run `FindMarker.CellDEEP`:

```{r cars, eval=FALSE}
#This is a test to see if the code is working, will reutrn 0 DE genes.
#For a actual test, please use data like: /datastore/Yiyi/datathon/Test_Dataset/covid_pDC_severeVShealthy.rds

pdc1 <- prepare_data(pDC, sample_id = "sample_id", group_id = "Worst_Clinical_Status", cluster_id = "initial_clustering", assay = "covid", Need.to.Norm_Transf = TRUE, Need.to.Scale = TRUE, Need.UMAP.generation = TRUE)
pdc2 <- prepare_data(pDC, sample_id = "sample_id", group_id = "Worst_Clinical_Status", cluster_id = "initial_clustering", assay = "covid")

#This code is for Seurat V5.
#Here, we drop out k clusters that has only 1 cell, add a dropout cell number.

#K-mean pooling:
de.test.1 <- FindMarker.CellDEEP(pdc1, Pool = FALSE, ident.1 = "Healthy", ident.2 = "Severe", group.by = "group_id", n_cells = 6, cell_cutoff = 10, assay = "RNA", pool_way = "kmean")
de.test.2 <- FindMarker.CellDEEP(pdc2, Pool = FALSE, ident.1 = "Healthy", ident.2 = "Severe", group.by = "group_id", n_cells = 6, cell_cutoff = 10, assay = "RNA", pool_way = "kmean")

de.test.1 <- FindMarker.CellDEEP(pdc1, Pool = TRUE, ident.1 = "Healthy", ident.2 = "Severe", group.by = "group_id", n_cells = 6, cell_cutoff = 10, assay = "RNA", pool_way = "random")
de.test.2 <- FindMarker.CellDEEP(pdc2, Pool = TRUE, ident.1 = "Healthy", ident.2 = "Severe", group.by = "group_id", n_cells = 6, cell_cutoff = 10, assay = "RNA", pool_way = "random")


#Randomly pooling:
de.test <- FindMarker.CellDEEP(pdc, Pool = TRUE, ident.1 = "Healthy", ident.2 = "Severe", group.by = "group_id", n_cells = 6, assay = "RNA", pool_way = "random")
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
